Avoiding tipping points in fisheries management: A Bayesian Non-Parametric approach

### 2014-06-06 manuscripts/manuscript.Rmd
revise sensitivity test

These results are not sensitive to the modeling details of the simulation.
The GPDP estimate remains very close to the optimal solution obtained
by knowing the true model across changes to the training simulation,
noise scale, parameters or structure of the underlying model, as seen in
Figure 7. The sensitivity analysis uses a factorial design of eight replicates 
of three different randomly generated parameter sets for each of two different 
generating models (Allen and Myers) over two different noise levels 
(0.01 and 0.05), for a total of 8 x 3 x 2 x 2 = 96 scenarios. In Figure 7, 
we pool results across different random seeds (111, 222,
333), noise values of 0.01 and 0.05 (not large enough to violate the
self-sustaining criterion of @Reed1979), and different randomly generated
parameters sets for each model, and using either the Myers or Allen as the
underlying structure.  While the GPDP performs slightly closer to optimal
on the smaller noise levels, and closer on the Allen model then the Myers
model, the differences are small compared to the values observed in using
the wrong parametric model.  The GPDP solution consistently avoids either
failing to harvest at all or crashing the stock, which results in the very
low values seen in parametric models in the previous figure. The
sensitivity analysis is compared against the optimal solution alone and
not shown against the estimates of the various parametric models (but
see Figure 6), where convergence of the Gibbs sampling could contribute
to their poorer performance if not checked by hand for each configuration.

@@

(following the Ahrenius relationship, see @Gardiner2009 for the derivation).
As a result, the impact of using a model which underestimates the risk of harvesting
past the critical point is much more severe, since this such a situation
occurs more often.  Conversely, with large enough distance between the
optimal escapement and unstable points relative to the noise, the chance
of a transition becomes vanishingly small and all models can be modeled
near-optimally. Models that underestimate the cost incurred by stock
sizes fluctuating significantly below the optimal escapement level will
not perform poorly as long as those fluctuations are sufficently rare.  Figure 7
shows that the GPDP is little effected by increasing noise or increasing Allee
effects over much of the range.

<!--FIXME the above para is not particularly convincing. Quantitative please? -->

>>>>

These results are not sensitive to the modeling details of the simulation.
The GPDP estimate remains very close to the optimal solution obtained
by knowing the true model across changes to the training simulation,
noise scale, parameters or structure of the underlying model. We consider
both a Latin hypercube approach and a more systematic investigation of the
parameters most responsible for impacting the transition rate: the relative 
distance to the Allee threshold and the noise effects.

The Latin hypercube approach systematically varies all combinations of
parameters, providing a more general test than varying only one parameter
at a time.  We loop across eight replicates of three different randomly
generated parameter sets for each of two different generating models
(Allen and Myers) over two different noise levels (0.01 and 0.05),
for a total of 8 x 3 x 2 x 2 = 96 scenarios. The Gaussian Process performs
nearly optimally in each case, relative to the optimal solution with no
parameter or model uncertainty (Figure S9, appendix).

@@

(following the Ahrenius relationship, see @Gardiner2009 for the derivation).
As a result, the impact of using a model which underestimates the risk of harvesting
past the critical point is much more severe, since this such a situation
occurs more often.  Conversely, with large enough distance between the
optimal escapement and unstable points relative to the noise, the chance
of a transition becomes vanishingly small and all models can be modeled
near-optimally. Models that underestimate the cost incurred by stock
sizes fluctuating significantly below the optimal escapement level will
not perform poorly as long as those fluctuations are sufficently rare.

Figure 7 shows that the GPDP is little effected by increasing noise or increasing
Allee effects over much of the range. Much larger stochasticity or higher Allee
effects make even the optimal solution without any model or parameter uncertainty
unable to harvest the population effectively (e.g. noise large enoug to violate the
self-sustaining criterion of @Reed1979). Only at the largest Allee effect
sizes are some replicates seen to deviate more from the optimal solution.
